Cloud Computing Data Capsule for Non-consumptive Text Analysis

### 2014-02-27 cloudpaper/paper.tex
added my text and incorporated version 3 of the paper

\title{Towards Non-Consumptive Cloud Computing for Digital Humanities}

\author{}

\maketitle
\begin{abstract}
As the amount of digitized archives grows, compute technology plays an increasing important role in digital humanities research. The advent of cloud computing offers researcher computation capabilities to process tens of thousands of archives which goes beyond their desktop machines can process. However, for copyrighted archives, it poses security challenges to the compute platform. In this paper, we investigate non-consumptive research, a research that allows user access copyrighted archives while prevents archives reconstruction during user access, in cloud computing. We build an infrastructure as a service (IaaS) cloud framework that makes use of data capsule to enforce non-consumptive research policy in virtual machine. This paper presents our architecture design and implementation details, and outlines next steps for future development.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.3.4}{Systems and Software}{Distributed systems}[cloud computing, data capsule]
%A category including the fourth, optional field follows...
\category{K.6.m}{Miscellaneous}{Security}[non-consumptive research]

@@

\keywords{Cloud computing, Non-consumptive research, data capsule} % NOT required for Proceedings

\section{Introduction}
As the amount of digitized archives keeps growing, researchers of digital humanities are facing with materials that they could ever hope to read in life time. For example, some researchers checked some of Ian Watt's claims against 3,600 novels between 18th and 19th century \cite{Example}. It is tedious, if possible, for human being to do this task by hitting the library stacks, checking out books and examining book contents. Therefore, digitized archives with computer access significantly changes the way digital humanities researchers perform research. Computer technology has been applied to facilitate digital humanities research on massive digitized materials. For instance, researchers run topic modeling algorithm on a set of digitized books to identify common topics among books \cite{LDA}, which cannot be discovered easily by just reading the books.

However, the massive amount of digitized texts also poses challenges on data analysis. First, compute capabilities required vary and depend on the analysis tasks as well as amount of texts. For example, running topic modeling algorithm generally requires more CPU cycles and memory than generating a word cloud based on word frequency. Fixed hardware setting of user desktop is not suitable to deal with such dynamic workloads. Second, high performance computing(HPC) provides a way for user to allocate resource dynamically based on her workload. However, HPC is batch oriented and digital humanities researchers usually need an interactive way to access the compute resources. Thus cloud computing is preferred in such case. Third, some of the digitized contents are copyrighted. Allowing user algorithms run directly on copyrighted texts opens a vulnerable channel that non-consumptive constraint may be violated. According to \cite{BookSettlement}, non-consumptive research is a research that no action or set of actions on the part of users, either acting alone or in cooperation with other users over the duration of one or multiple sessions can result in sufficient information gathered from a collection of copyrighted works to reassemble pages from the collection. In other words, a user may steal copyrighted content while she runs her algorithm. We extend the definition above to include the situation that a user computer is compromised by malicious programs which acts on user\rq s behave to steal copyrighted content.

We propose a non-consumptive cloud framework to address challenges mentioned above. On one hand, cloud computing, which has elastic computing feature, is a natural fit for various analysis tasks. Researcher can create virtual machines shipped with different compute capabilities based on the need. Once the analysis is done, virtual machine is wiped out and resources are released for other users to share. On the other hand, the virtual machine of our framework is equipped with data capsule \cite{Borders:2009:PCD:1855768.1855791} to provide non-consumptive policy to prevent copyrighted leakage under the assumption that virtual machine is compromised. In data capsule, one virtual machine has two modes, i.e. maintenance mode and secure mode. In maintenance mode, user can access network and install software freely, but cannot access copyrighted texts. In secure mode, copyrighted texts become accessible to user while network access and file system access are highly constrained. Users are only allowed to access a predefined set of network addresses and write to a specific volume which is only visible in secure mode. Every other changes user made to the system in secure mode, except for the ones made to special volume, is lost when mode is switched from secure to maintenance. This is guard against the situation that copyrighted texts is saved in VM in secure mode and copied out through network in maintenance.

Our framework is implemented as a sub system within HathiTrust Research Center (HTRC) \cite{HTRC}. HTRC aims at enabling computational access for nonprofit and educational users to perform research on digitized texts. Through various services and tools provided from HTRC, user can access digitized texts, and run text mining algorithms on HTRC compute resources.

This paper is organized as follows. Section \ref{title:related} summaries related work. Section \ref{title:overview} presents an overview of HTRC and data capsule, and identifies the design requirements for our system. Section \ref{title:design} describes details of our system design and implementation. Section \ref{title:future} outlines future work and section \ref{title:conclusion} concludes.

@@

Researchers have already leveraged the power of cloud computing in digital archives. Teregowda et al. employed cloud computing as underlying infrastructure for CiteSeerX, which is a public search engine and digital library for scientific and academic papers \cite{Teregowda:cloud}. Rosenthal et al. investigated the usage of cloud in their digital preservation system -- LOCKSS for libraries \cite{Rosenthal:preservation}. Our system differs from those systems in the sense that we investigate and promote non-consumptive research in the cloud platform.

Generally speaking, cloud computing can be categories as SaaS (software as a service), PaaS (platform as a service), and IaaS (infrastructure as a service) \cite{Armbrust:EECS-2009-28}. Our cloud framework intends to provide a weaker form of IaaS (infrastructure as a service). That is user can configure some of the VM specs, e.g., operation system, number of CPU, memory, and disk, but not the network, nor the volume. There are numbers of existing cloud platforms support IaaS, either in a commercial way or in an open source way. Amazon EC2 \cite{EC2} is probably the most well-known IaaS platform.  On regard to open source cloud platform, Eucalyptus \cite{Nurmi:2009:EOC:1577849.1577895} is an open source IaaS platform that provides Amazon compatible cloud environment. OpenStack \cite{OpenStack} is another open source IaaS platform that gains increasing popularity. Researchers investigated different cloud platforms \cite{Sempolinski:cloud,vonLaszewski:2012:CMC:2353730.2353779}. The reasons we do not build our system on existing open source platforms are two folds. First, existing cloud platforms introduce numerous complexities for the data capsule which enforces non-consumptive research policy in VM. Those complexities are from unnecessary features for digital humanities researchers. For example, researcher does not need to configure a software defined network to run her text mining algorithms. Second, existing cloud platforms are designed for general purpose and expose many vulnerable channels. For example, allowing user to configure network would pose significant threats to our systems. Therefore, instead of using existing cloud platform, we build a cloud framework around data capsule, which satisfies digital humanities researchers\rq need and non-consumptive research requirement. Our research also illuminates the path that data capsule could potentially be applied to more general cloud platforms.

Related work of Data Capsule.

\section{Overview} \label{title:overview}
This section presents background of HathiTrust Research Center (HTRC), data capsule and identifies threat model as well as design requirements for our system.

\subsection{HathiTrust Research Center Background} \label{subtitle:background}
HTRC consists of number of services that facilitate nonprofit and educational users to access and research on texts from HathiTrust Digital Library. Figure \ref{fig:htrc} below shows an overview of HTRC from an interaction point of view. HTRC provides users with a complexity hiding interface, left bar on Figure \ref{fig:htrc}, which shadows HTRC service complexity. The central cloud shape represents the entire HTRC system which can be divided into 4 categories: 1) metadata and data subsystem which provide metadata, raw text, and statistical information access; 2) data mining subsystem that embraces several tools for users to mine corpus; 3) job execution subsystem that runs various text mining algorithms on HPC environment; 4) auxiliary services subsystem that supports other services, e.g., user authentication service.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.3]{figures/htrc}
  \caption{HathiTrust Research Center Infrastructure.}
  \label{fig:htrc}
\end{figure}

@@

The system is designed to allow user to access copyrighted data in a compromised operating system which runs in a virtual machine (VM). Neither the operating system, the driver, nor the applications (except for user’s application running against HTRC Data service) are trusted. Although our system allows arbitrary behaviors in VM, it does require some trusted components. The virtual machine monitor (VMM) that runs virtual machines is part of the trusted computing base (TCB). The hosts where VMM locates are also part of the TCB. The internal network among VMs is part of the TCB, i.e., firewall policy is sufficient to prevent attack from one VM to another one. User’s application that runs against HTRC Data service is considered trustworthy, although it could potentially encode the copyrighted data and deliver it as final result. We require user to sign a legal agreement before she uses our system. We intend to add some result analysis to automatically detect data leakage and leave this as future work.

\subsection{Data Capsule}

The data capsule was developed by Borders et al. \cite{Borders:2009:PCD:1855768.1855791}. It enforces two modes on a single virtual machine, i.e., maintenance mode and secure mode, to provide secure access to sensitive data. In maintenance mode, user is free to access internet and install software in VM. While in secure mode, sensitive data stored in a secure volume will be attached to the VM and become visible to user. The network access is blocked in secure mode to prevent data leakage by network. When user switches from secure mode to maintenance mode, changes made to places other than volume are wiped out so that sensitive data cannot leak through copying to local disk neither. Only changes made to volume is persistent. Therefore, in data capsule, user can access sensitive data and leakage cannot take place neither through network channel nor through disk.

Data capsule was mainly developed for general usage in single machine. We adapt and extend data capsule based on the context of HTRC. Sensitive data in HTRC is copyrighted text which is exposed through a API in Restful web service instead of staying in volume. Data capsule needs to enable the network channel between web service serving data and virtual machine. On regard to future HTRC services, data capsule should have a flexible network control mechanism. Besides, to carry out analysis tasks, researchers need persistent storage to store temporal results for iterative analysis purpose. Thus, the role of secure volume in data capsule is changed from mainly serving read to mainly serving write. In addition, data capsule is designed to work in single machine. To provide a cloud environment across multiple machines to multiple researcher, we need another layer on top of data capsule to coordinate different machines. We propose a web service layer, which is responsible for management effects e.g., resource allocation, request scheduling, status maintenance, and etc, on top of the data capsule to implement the cloud environment. Section \ref{title:design} gives details of design and implementation of data capsule in HTRC context.

\subsection{Design Requirements} \label{subtitle:requirement}
Our non-consumptive cloud framework falls into the second category mentioned in section \ref{subtitle:background} through provisioning a secure environment for user to conduct research against our data, probably copyrighted. We target digital humanities researchers and aim at providing a user friendly environment for user to access copyrighted text while preventing copyrighted text leakage. We identify following design requirements.
\begin{enumerate}
  \item It provides a cloud environment that makes better use of our backend resources;
  \item It prevents texts copied out from our system through network, and interference among users;
  \item It audits users activities;
  \item It is easy for researchers to use. Researchers have the privilege to configure the software and hardware environment to meet their needs;
  \item It can support large scale data process paradigm, e.g., MapReduce.
\end{enumerate}

\section{Design and Implementation} \label{title:design}
This section presents the details of the architecture and implementation of our system.

\subsection{Architecture}

Figure \ref{fig:architecture} delineates our architecture design. It consists of three layers, physical layer, web service layer and web front end layer from bottom to top. The physical layer includes physical machines and hypervisor software that run virtual machines. It also includes the data capsule implementation which is scripts that wrap hypervisor commands to perform multiple tasks. Database, image store and volume store also sit in this layer. Database is used by the web service to maintain persistent states for virtual machines and different operations. Virtual machine images as well as secure volumes locate in NFS, a share file system. The web service layer is the central controller of the system. It is responsible for resource allocation, request scheduling, state maintenance, and failover on physical layer. It also has an audit component to log user activities. Finally we expose the system through the web font end layer. It consists of a web UI where user interacts with our system and a user authentication server which validates user identification. To validate user identity, we use OAuth 2.0 \cite{OAuth2} for user authentication.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.33]{figures/layers}
  \caption{Overall architecture design.}
  \label{fig:architecture}
\end{figure}

\subsection{Workflows}
This section presents control flows within our system components.

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.35]{figures/workflow-control}
  \caption{System control flow.}
  \label{fig:control}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.45]{figures/workflow-HTRCData}
  \caption{Virtual machine access flow.}
  \label{fig:vmaccess}
\end{figure}

@@

@@

In summary, our architecture fulfills the design requirements in section \ref{subtitle:requirement}. First, the web front end and web service use OAuth 2.0 to authenticate user which denies unauthorized users. Second, web service coordinates a number of machines equipped with data capsule to provide a cloud environment and log all user activities. Through the log files, we are able to tell who did what. Third, the data capsule blocks network channels when VM is in secure mode so that no copy out can take place. Forth, researcher can manage and manipulate her virtual machines through a simple web UI which is more user friendly than a command line tool. Besides, researcher can log in to virtual machine through VNC which provisions GUI desktop instead of terminal. In addition, researcher is allowed to configure the hardware setting when creating the VM from web UI and software setting in VM in maintenance mode to meet her needs. These effects help lower the usage burdens for digital humanities researchers. Last but not least, the web service can setup a Hadoop cluster for researcher to run MapReduce jobs although more efforts are needed to configure data capsule properly in a MapReduce context. We leave it as future work.

@@

\subsubsection{Physical layer implementation}
Under construction.

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}

>>>>

\title{Cloud Computing Data Capsule for Non-consumptive Text Analysis}

\numberofauthors{8}
\author{
\alignauthor
Jiaan Zeng \\
       \affaddr{School of Informatics and Computing Indiana University}\\
       \email{jiaazeng@indiana.edu}
\alignauthor
Guangchen Ruan \\
       \affaddr{School of Informatics and Computing Indiana University}\\
       \email{gruan@indiana.edu}
\alignauthor 
Alex Crowell \\
       \affaddr{Department of Computer Science and Engineering University of Michigan}\\
       \email{crowella@umich.edu}
\and  % use '\and' if you need 'another row' of author names
\alignauthor 
Atul Prakash \\
       \affaddr{Department of Computer Science and Engineering University of Michigan}\\
       \email{aprakash@umich.edu}
% 5th. author
\alignauthor Beth Plale \\
       \affaddr{School of Informatics and Computing Indiana University}\\
       \email{plale@indiana.edu}
}

\maketitle
\begin{abstract}
As digital archives grow in size, the interest by humanities and informatics
researchers alike increases in computational investigation of a corpus.  The
cloud computing model of ``data as a service'' which co-locating computation with
a data collection of value, allows for scales of computational analysis that
far exceeds what a desktop machine can provide. However, when data collections
are protected, such as digitized books are through copyright, there are
additional challenges to provisioning an analytical framework. We investigate
issues in text analysis on a protected corpus in a cloud environment that
prevents reconstruction of part or whole of the corpus.  The proposed framework
makes use of a novel notion of "data capsule" to enforce non-consumptive
research policy using virtual machines.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.3.4}{Systems and Software}{Distributed Systems}[Cloud Computing, Storage Capsules]
%A category including the fourth, optional field follows...
\category{K.6.m}{Miscellaneous}{Security}[Non-consumptive Research]

@@

\keywords{Cloud computing, Large-scale Text Mining, Non-consumptive Research, Storage Capsules} % NOT required for Proceedings

\section{Introduction}
As increasing amounts of digitized text become available from sources such as university libraries, researchers encounter access to more material than they could ever hope to read in life time, creating opportunities for new forms of research. For example, research has checked literary critic Ian Watts' claims against 3,600 novels written between the 18th and 19th centuries \cite{Example}. While this tedious task could be carried out by hand, digitized texts coupled with text mining tools, enables new discoveries.  One can apply topic modeling such as Latent Dirichlet allocation (LDA)~\cite{LDA}) at the book level to narrow from millions of texts to a few thousand, then page level LDA to zero down to relevant pages, effectively expanding the reach of research investigation of the informatics or digital humanities researcher.

Texts digitized from research libraries have restrictions on their use; most obviously copyright for content that is post about 1923.  While most in the legal community would agree that text mining qualifies as fair use, the text mining cannot as a byproduct leak entire books to web pages.  This kind of limited analytical use on the data we call \textit{non-consumptive research}.  Non-consumptive research we define as \textit{No action or set of actions on the part of users, either
acting alone or in cooperation with other users over the duration of one or multiple sessions can result in sufficient information gathered from a collection of copyrighted works to reassemble pages from the collection.}

In this paper we propose a novel solution to non-consumptive research that uses a data capsule approach~\cite{Borders:2009:PCD:1855768.1855791} preventing misuse.  The work is being carried out in the context of the HathiTrust Research Center~\cite{HTRC}, a set of software and services that currently provide text analysis capability over public domain books.  HTRC is in the process of securing access to 12 million volumes of text data and images from research libraries across the country.

Text analytics over a large corpus of sensitive data poses challenges for several reasons. First, text mining tools vary in their computational demand. Analysis could take the form of simple access to a database of features; could involve a linear traversal through digitized text; or could be a computationally intensive natural language processing task like LDA.    Second, while high performance computing (HPC) gives a user resources dynamically based on workload, HPC systems remain largely batch oriented which is out of phase with digital humanities researcher requiring high levels of interaction with texts. The cloud computing data-as-service model avoids the problem of limited interactivity. Third, and the biggest challenge of the three, is that digitized texts can have restrictions on their access.  Allowing interactive access on texts user algorithms run directly on copyrighted texts opens a vulnerable channel that non-consumptive constraint may be violated.

We propose a non-consumptive cloud framework for data analytics on sensitive corpora.   Using a remote virtual machine (VM) model, researchers can build a VM configured with software and tooling based on their need. Once an analysis is finished, the VM is wiped out and resources released for other users to share. VMs offer no inherent protection, however.  Our approach extends the virtual machine by turning it into a \textit{data capsule}\cite{Borders:2009:PCD:1855768.1855791} that prevents leakage of copyrighted content in the event that the VM is compromised or data analysis routines malicious.  The HTRC Data Capsule provides the virtual machine with two modes: a maintenance mode during which a user can access the network and install software freely, but cannot access copyrighted data; and secure mode where copyrighted texts become accessible to user while the network access and file system access is highly constrained. In the latter mode, users are allowed only  access to a predefined set of network addresses and write to a specific volume which is only visible in secure mode. Every other changes user made to the system in secure mode, except for the ones made to special volume, is lost when mode is switched from secure to maintenance. This is to guard against the situation that copyrighted texts is saved in VM in secure mode and copied out through network in maintenance.

This paper introduces the architecture and design of the HTRC Data Capsule.  The research question driving HTRC Data Capsule imposes five major requirements as follows:

\begin{itemize}
\item Non-consumptive research: that is, provides safe handling of large volumes of data, and
can ensure that the read restrictions of the definition hold
\item Openness: users are not limited to using a known set of algorithms, and instead are
expected to experiment with their own algorithms
\item Efficiency: It is not possible to analyze algorithms for conformance prior to
execution
\item Low cost and scale:  Run at large-scale and low cost to users
\item  Long term and broad value:  framework is designed for adoption for other
purposes
\end{itemize}

%Jiaan,  these above are the requirements from the proposal.  These replace the requirements that were in Sec 3, which were much more implementation focused and not appropriate for a research paper.

This paper is organized as follows: Section \ref{title:related} summaries related work and \ref{title:overview} presents an overview of HTRC and data capsule, and identifies the design requirements for our system. Section \ref{title:design} describes details of our system design and implementation. Section \ref{title:future} outlines future work and section \ref{title:conclusion} concludes.

@@

Research that leverages the power of cloud computing for text analysis has been done. Teregowda et al. employ cloud computing as underlying infrastructure for CiteSeerX, which is a public search engine and digital library for scientific and academic papers \cite{Teregowda:cloud}. Rosenthal et al. propose LOCKSS for digital preservation; LOCKSS uses a cloud model in their digital preservation system~\cite{Rosenthal:preservation}. Our system differs from those systems because of the protection requirements of non-consumptive research in the cloud platform.

There are numerous cloud platforms that support IaaS, either commercially or in open source. Amazon EC2 \cite{EC2} is probably the most well-known IaaS platform, but there is Eucalyptus \cite{Nurmi:2009:EOC:1577849.1577895}, and OpenStack \cite{OpenStack}. Researchers investigated different cloud platforms \cite{Sempolinski:cloud,vonLaszewski:2012:CMC:2353730.2353779}. We do not build our system on existing open source cloud platforms for two reasons: first, existing cloud platforms introduce numerous complexities for the data capsule which has to enforce the non-consumptive research policy in the VM. The complexities stem from avoiding imposing unnecessary burdens on the digital humanities researcher. For example, the researcher should not need to configure a software defined network to run her text mining algorithms. Second, existing cloud platforms are designed for general purpose and expose many vulnerable channels. For example, allowing user to configure network would pose significant threats to our systems. Therefore, instead of using existing cloud platform, we build a cloud framework around data capsule, which satisfies digital humanities researchers\rq need and non-consumptive research requirement. Our research also illuminates the path that data capsule could potentially be applied to more general cloud platforms.

Storage capsules \cite{Borders:2009:PCD:1855768.1855791} is a mechanism for
containing sensitive data within a virtualized environment with the goal of
minimizing the available channels to leak that data.  Although storage capsules
provide no guarantees on the integrity of the stored data -- which could be
modified or deleted by an attacker -- this poses little issue when storage
capsules is applied to non-consumptive research, where the copyrighted source
data can simply be made read-only.  Additionally, the storage capsules design
is well-suited to non-consumptive research, in that it is able to maintain
strong security guarantees on the sensitive data while being highly permissive
to users, who may need to install custom software or perform other actions that
would require the granting of many privileges in a normal environment.  The
application of storage capsules we present in this paper currently does not
provide the same level of protection against covert channels that is provided
in the original storage capsules system, but improvements in the implementation
are being made that will eventually provide greater protection than that given
in the original work.

\section{Overview} \label{title:overview}
This section presents background of the HathiTrust Research Center software and services, data capsule and identifies threat model as well as design requirements for our system.

\subsection{HathiTrust Research Center Background} \label{subtitle:background}
The HathiTrust Research Center is a set of software and services to carry out computational analysis using digitized books from the HathiTrust Digital Library for research and educational use.
Figure \ref{fig:htrc} is a cartoon diagram of the system.  A researcher accesses the system through one or more front ends (shown on right).  The system in its simplest form satisfies a user need by constructing for the user a \textit{Workset} representing selected text mining tools, selected subsets of data from either the HathiTrust digital repository, or from feature sets that have been extracted in advance, and data from other sources.   This Workset bundle is executed on a large-scale compute resource.   As is shown by the arrow pointing to both compute resource and front end (complexity hiding interface), text analysis is a highly interactive process, thus challenging the use of HPC resources shown, even if, like Big Red 2 at Indiana University, they are architected to handle data-intensive computations.  The HTRC system is modularly architected using a web services paradigm (i.e., REST interfaces).  It utilizes a Solr index, Cassandra noSQL store, both of which are sharded across half-dozen machines for higher replicability and availability.  Analytical tools include the SEASR suite of text mining tools, with ongoing extension of support to R and i-Python.

The HTRC architecture uses OAuth2 authentication and has an auditing service.   While this architecture is adequate for analysis algorithms that have been vetted by HTRC, it cannot support analysis algorithms that originate with an external researcher.  This latter issue is the purview of the HTRC Data Capsule.

\begin{figure}[tbh]
  \centering
  \includegraphics[scale=0.3]{figures/htrc}
  \caption{Functional diagram of HathiTrust Research Center software and services}
  \label{fig:htrc}
\end{figure}

\subsection{Storage Capsules}

Storage capsules is a system developed by Borders et al.
\cite{Borders:2009:PCD:1855768.1855791} that allows privileged access to
sensitive data while also restricting the channels through which that data can
be released.  Capsules uses virtual machine snapshotting and simple
policy-based restriction mechanisms to allow a user to enter a ``secure'' mode,
where network and other data channels are restricted in exchange for access to
the data being protected.  After using the protected data, when the user
returns to normal use of the system, which we call ``maintenance'' mode, all
changes to the system except those made to the designated secure data are
forgotten, and the system returns to the state it was in before the switch to
secure mode, thereby regaining full Internet access and the ability to make
persistent changes to the virtual machine, such as installing software.  In
this way, network and storage channels cannot be used to leak the sensitive
data.  This usage model is readily applicable to non-consumptive research, in
that a researcher can administer their system (e.g. install any required
software tools) and then switch to ``secure'' mode to perform their analysis.

Because storage capsules was originally developed with use on a personal
machine in mind, it had to be adapted and extended to work within the HTRC
cloud environment. In HTRC, sensitive data is copyrighted text that is exposed
through a Restful web service API instead of within a machine. Storage capsules
manages the network channel between virtual machines and the web services
serving data to them. In consideration of potential future HTRC services,
storage capsules has a flexible network control mechanism that allows network
policies for different modes to be written by administrators.

Additionally, in order to provide a cloud environment across multiple machines
and to a large number of researchers, there is a need for another layer on top
of storage capsules that coordinates different machines. We therefore
implemented a web service layer that is responsible for management of virtual
machines (e.g., resource allocation, request scheduling, status maintenance)
above the storage capsules layer.  Section \ref{title:design} gives details of
the design and implementation of storage capsules and the web service layer in
the context of HTRC.

@@

Under our usage model, users access the copyrighted data through remotely
accessed virtual machines that read the data from a network-accessed data
service.  The virtual machine presented by the user is not a part of the trusted
computing base (TCB).  We assume the possibility of malware being installed as
well as other remotely initiated attacks on the VM.  These attacks could
potentially compromise the entire operating system and install a rootkit that
are undetectable to the end user.  The end users themselves are considered to
act in good faith, but this does not preclude the possibility of them
unwittingly allowing the system to be compromised.  We believe this is a
reasonable assumption since users are required to sign a legal agreement before
using our system.  Beyond the virtual machine itself, the virtual machine
manager (VMM) and the host it runs on are both trusted, and fall within the TCB.
This includes system services that enforce network and data access policies for
the virtual machines.  Finally, the HTRC Data service itself is also a part of
the TCB.

Users have VNC access to their virtual machines so that they have a graphical
interface to the machine.  However, this access does admittedly provide a
channel for potential data leak.  For now, we apply our assumption that the end
user acts in good faith, and also assume that they are the only one accessing
the virtual machine.  For future work, we can use analysis of the channel as a
means to automatically detect potential abuses of it for data leak purposes.
Additionally, a channel is provided to the user for releasing results when their
research is complete.  Although we currently intend to allow released results to
be downloaded via a link sent to the end user's email inbox, we note that the
released data could also be subjected to manual or automated review to detect
potential abuses.  We also leave this for future work.

Another potential threat is that of covert channels between virtual machines
that run on the same host machine.  For instance, a virtual machine running in
secure mode could possibly make use of such covert channels to leak data to a
coresident virtual machine running in maintenance mode, which can in turn leak
the data anywhere it pleases.  We acknowledge that this could pose a serious
threat, but leave addressing it for future work.

\section{Design and Implementation} \label{title:design}

 The high level architecture of the HTRC Data Capsule, see Figure \ref{fig:architecture}, consists of three layers shown bottom to top: a physical layer, a web service layer and web front-end layer. The physical layer consists of physical machines and hypervisor software that run the virtual machines of the data capsule. It also includes the data capsule implementation which is scripts that wrap hypervisor commands to perform multiple tasks. Database, image store and volume store also sit in this layer. The database is used by the web service layer to maintain persistent states for virtual machines and different operations.

Virtual machine images as well as secure volumes locate on NFS, a distributed file system. The web service layer is the central controller of the system. It is responsible for resource allocation, request scheduling, state maintenance, and failover on physical layer. It also has an audit component to log user activities. Finally we expose the system through the web font end layer. It consists of a web UI where user interacts with our system and a user authentication server which validates user identification. To validate user identity, we use OAuth 2.0 \cite{OAuth2} for user authentication.

\begin{figure}[ht]
  \centering
  \includegraphics[scale=0.33]{figures/layers}
  \caption{HTRC Data Capsule architecture}
  \label{fig:architecture}
\end{figure}

\subsection{Workflows}

There are three major control flows within the HTRC Data Capsule system:   virtual machine creation, authentication, and VM access.  Each are described in turn.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[scale=0.35]{figures/workflow-control}
  \caption{System control flow.}
  \label{fig:control}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[scale=0.45]{figures/workflow-HTRCData}
  \caption{Virtual machine access flow.}
  \label{fig:vmaccess}
\end{figure}

@@

%Jiaan,  this section needs to tie back around and wrap in the requirements laid out in section 1.  The implementation requirements in Sec 3 are now gone.  In addressing the broader goals in Sec 1,  how well does the work so far address these requirements?  What's been done and what hasn't been addressed (for instance: we haven't tried for generality yet.)  This is still a 'towards' paper so can and should be honest about where we are and where open work still exists

@@

First, the web front end and web service use OAuth 2.0 to authenticate user which denies unauthorized users. Second, web service coordinates a number of machines equipped with data capsule to provide a cloud environment and log all user activities. Through the log files, we are able to tell who did what. Third, the data capsule blocks network channels when VM is in secure mode so that no copy out can take place. Forth, researcher can manage and manipulate her virtual machines through a simple web UI which is more user friendly than a command line tool. Besides, researcher can log in to virtual machine through VNC which provisions GUI desktop instead of terminal. In addition, researcher is allowed to configure the hardware setting when creating the VM from web UI and software setting in VM in maintenance mode to meet her needs. These effects help lower the usage burdens for digital humanities researchers. Last but not least, the web service can setup a Hadoop cluster for researcher to run MapReduce jobs although more efforts are needed to configure data capsule properly in a MapReduce context. We leave it as future work.

@@

\subsubsection{Physical layer implementation}

The backend that manages virtual machines is implemented as a set of Linux
shell scripts that manage the \texttt{qemu} VMM in order to implement the
functionality of storage capsules.  These scripts are remotely run by the web
service via a secure shell (SSH) connection.  \texttt{qemu} provides live
snapshotting functionality that serves an important role in realizing our
storage capsules implementation.  When a user transitions to secure mode, a
snapshot is taken of the entire virtual machine state via the backend scripts,
and any further use of the system is recorded in memory and does not persist
upon shutdown or any other operation.  Upon return to maintenance mode, the
snapshot taken earlier is restored, and all system progress that followed it is
forgotten.

Virtual machines are isolated from the rest of the host's networking through the
use of a tap interface.  Their connection is then bridged to host networking.
Network policies for both modes are implemented using iptables rules.  These
rules can be written in custom policy files that can be specified on mode
switch, allowing for any arbitrary policy desired by the administrator.  In
addition to the policy rules, some basic rules are always enforced, for example
preventing communication between virtual machines residing on the same host.

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This research funded through a grant from the Alfred P. Sloan Foundation, grant \# xxxxxx
%ask Nicole to give you the grant number; I'm not finding it.   This needs to be the number the Sloan foundation knows, not IU's internal grant #
